### 2014-04-14 doc/uist14/iteration1.tex
refined iteration1, didn't touch qualitative feedback

\section{Iteration 1: IR vs. List}
Our system design uses IR as the beam cursor for physical target selection because the area coarse selection will remove the targets outside of users' view range. And this could help during the fine selection time because there is a smaller set of targets for fine selection. The opposite is to have a complete list of all targets when there is no single coarse selection and the disambiguation is always needed. This brought up the first question that we asked ourselves -- {\em how much does using IR help in reducing the selection time}. To answer that question and quantify the benefit of having IR for the coarse selection, we carried out our first target acquisition study which compares the {\em IR selection} and {\em list selection}.

@@

In the within-subject study, half of them performed {\em IR selection} first and the other half did {\em list selection} first. For each selection condition, we conducted 15 target selection by random choosing from all the targets. During the study, we measure the {\bf target acquisition time} for each target selection, and afterwards, participants were asked to complete a survey that elicited answers to Likert-scale questions as well as open-ended answers about their experience.

@@

To further understand if the gain comes from the coarse selection, we splited the data from {\em IR selection} to two parts -- ones that require disambiguation and ones that don't. The result is shown in Figure~\ref{fig:selection-time}A. It shows that it takes 6.40 seconds (on average) to complete the connection if coarse selection has achieved the acquisition, while when multiple devices are in range, the time increases to 9.16 seconds, indicating additional 2.76 seconds for disambiguation. Though it takes significantly longer ($t(19)=-2.7827, p=0.012$ using t-test) in the latter case, they only happen 10\% of total {\em IR selection} trials.

@@

To further generalize the results, in Figure~\ref{fig:time-vs-list-order}, we show the acquisition time for each individual target in {\em list selection} condition, ordered by their relative position in the list. Since with IR technique, the acquisition time is invariant from each target's order, we use solid lines to represent the average performance of {\em IR selection}. From this figure, we can see that once the target's order is larger than 6, the average acquistion time will be larger than the case when disambiguation is needed in {\em IR selection}. Therefore, we argue that once there are more targets in the physical space, the {\em list selection} is not scalable.

>>>>

\section{Iteration 1: IR vs. List}
Our system design uses IR as the beam cursor for physical target acqusition because the area coarse selection filters out the targets outside of the user's view range. This help during the fine selection time because there is a smaller set of targets to select from. The opposite is to have a complete list of all targets when there is no coarse selection and the disambiguation is always needed. This brought up the first question that we asked ourselves -- {\em how much does using IR help in reducing the selection time}. To answer that question and quantify the benefit of having IR for the coarse selection, we carried out our first target acquisition study which compares the {\em IR selection} and {\em list selection}.

@@

In the within-subject study, half of them performed {\em IR selection} first and the other half did {\em list selection} first. For each selection condition, we conducted 15 target selection by randomly choosing from all the targets. During the study, we measure the {\bf target acquisition time} for each target selection, and afterwards, participants were asked to complete a survey that elicited answers to Likert-scale questions as well as open-ended answers about their experience.

@@

To further understand if the gain comes from the coarse selection, we splited the data from {\em IR selection} into two parts -- ones that require disambiguation and ones that don't. The result is shown in Figure~\ref{fig:selection-time}B. It shows that it takes 6.40 seconds (on average) to complete the connection if coarse selection has achieved the acquisition, while when multiple devices are in range, the time increases to 9.16 seconds, indicating additional 2.76 seconds for disambiguation. Though it takes significantly longer ($t(19)=-2.7827, p=0.012$ using t-test) in the latter case, they only happen 10\% of total {\em IR selection} trials.

@@

To further generalize the results, in Figure~\ref{fig:time-vs-list-order}, we show the acquisition time for each individual target in {\em list selection} condition, ordered by their relative position in the list. Since with IR technique, the acquisition time is invariant from each target's order, we use solid lines to represent the average performance of {\em IR selection}. From this figure, we can see that once the target's order is larger than 6, the average acquistion time will be larger than the case when disambiguation is needed in {\em IR selection}. Therefore, we argue that once there are more targets in the physical space, the {\em list selection} method is not scalable.
